Afzal Alam

Phone: 8102061851 | Email: afzalalam.afzuu@gmail.com | LinkedIn: linkedin.com/in/afzal-alam-
afzuu

PROFESSIONAL SUMMARY
Highly skilled and results-driven Full-Stack Developer with extensive expertise in the MERN Stack,
Laravel, and Flutter frameworks. Proven track record in architecting high-performance, scalable
systems and executing complex AI/RAG pipelines to deliver cutting-edge solutions. Demonstrated
proficiency in optimizing memory management via Redis and deploying highly available
applications on AWS and Vercel infrastructure. Passionate about building robust, user-centric ERP,
LMS, CMS, and E-commerce platforms that drive business growth and user engagement.
TECHNICAL SKILLS
Languages & Frameworks: Node.js, Express.js, React.js, Next.js, Laravel, Flutter, Django,
JavaScript (ES6+), PHP
Databases & Caching: MongoDB, PostgreSQL, MySQL, Redis (Expert in Caching & Performance
Optimization Strategies)
DevOps, Cloud & Security: AWS (EC2, S3), Vercel, Git/GitHub, API Security (JWT, OAuth 2.0,
Rate Limiting)
AI & LLM Integration: Retrieval-Augmented Generation (RAG) Architectures, LLM Integration for
Content Generation, Prompt Engineering
PROFESSIONAL EXPERIENCE

Full-Stack Developer | SchoolDigitalised
April 2026 – Present
Spearheading the development of large-scale, high-traffic E-commerce, EdTech (LMS), and
CMS solutions, consistently supporting 5,000+ concurrent active users.
Architecting highly available backend systems specifically designed for live-class conduction
and VOD (Video-on-Demand) storage, successfully reducing system latency by 20% through
strategic cloud optimization.
Collaborating with cross-functional teams to translate complex business requirements into
scalable technical architectures.
•

•

•

Full-Stack Developer | Microcen Pvt Ltd
Successfully built and maintained complex ERP, LMS, and CRM solutions, achieving a
consistent 99.9% system uptime over a 12-month period.
Applied advanced API lifecycle management and enforced strict security protocols, resulting in
a significantly more resilient infrastructure.
Optimized complex multi-database queries (MySQL/PostgreSQL/MongoDB), which improved
overall system response time by 30% for end-users.

Web Developer Intern | Niks Technology Limited
July 2021 – Present (5 yrs 1 mo) | Patna, Bihar, India
Gained valuable hands-on experience in web development workflows, including designing responsive layouts and implementing client-side interactivity.
Collaborated with senior team members on frontend and backend implementations using modern web technologies.
Successfully contributed to the development and optimization of various web applications, serving as a highly interesting learning experience.
KEY PROJECTS

1. AI-Driven Affiliate & Content Platform
Built a comprehensive, high-performance affiliate aggregator from the ground up using Next.js
and PostgreSQL.
Executed seamless integration of multiple third-party Affiliate APIs, ensuring robust error
handling and data consistency.
Enforced AI (LLM) workflows to automate high-quality, SEO-optimized blog generation.
Optimized user search performance via AI-driven indexing; successfully monetized the platform
via AdSense, leading to a 40% increase in organic site traffic.
2. High-Concurrency Online Exam System (Performance Focused)
Engineered a highly scalable exam architecture using Redis to provide real-time, high-speed
memory management.
Executed high-volume data caching of critical exam activities (answers/submissions) in Redis,
which minimized direct database load by 50% during peak events.
Applied automated submission logic triggered on session timeouts, ensuring 100% data
integrity for over 10,000+ simultaneous test submissions.
3. Cross-Platform Mobile Ecosystem
Developed a highly feature-rich, responsive mobile application ecosystem using Flutter, with a
secure, high-performance Laravel backend.
Enforced robust API request protection and secure authentication flows using
SharedPreferences for seamless token management, serving 50k+ active users.
4. Scalable E-commerce Application
Designed and developed a comprehensive full-stack e-commerce platform leveraging the full
power of the MERN Stack.
•

•

•

•

•

•

Web Developer
Niks Technology Limited . Internship
Jul 2021 - Present . 5 yrs 1 mo
Patna, Bihar, India

It was an interesting learning experience for me
•

•

•

•

•

•

•

Managed the end-to-end deployment process on AWS infrastructure, ensuring high availability,
load balancing, and peak performance for a global user base.
EDUCATION & CERTIFICATIONS
Bachelor of Computer Applications (BCA)
Certifications: Professional Certifications in Advanced Web Development and AI Integration
(LinkedIn Learning and Udemy).